What do incoming university students believe about open science practices in

### 2021-09-28 analysis/Manuscript.Rmd
Integrated Google Docs copy with RMarkdown

---
title: What do incoming university students believe about open science practices in
  psychology?
author:
- name: Jennifer L. Beaudry
  affiliation: '1'
  corresponding: yes
  address: Postal address
  email: jbeaudry@swin.edu.au
  role: null
- name: Michael C. Philipp
  affiliation: '2'
  role: null
- name: Matt N. Williams
  affiliation: '2'
  role: null
shorttitle: Psychology students' beliefs about open science
output:
  papaja::apa6_word: default
  papaja::apa6_pdf: default
authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
  Enter author note here.

# Abstract: |

## BACKGROUND: Rapid changes to methodological best practices present significant challenges for educating students new to the field of psychology. Some students may have existing knowledge about recent methodological reforms (e.g., preregistration, replication). Yet, where knowledge is lacking, overemphasizing the problems that precipitate these reforms (e.g., p-hacking, HARKing) may lead students to de-value scientific methods as a credible means for generating knowledge. 
## OBJECTIVE: Understanding students’ naive conceptions about how science works and the norms that guide scientific best practice is important so that teachers can adapt their teaching to the students’ existing understandings. 
## METHOD: This study examined ### incoming undergraduate psychology students’ understandings of how research *should* be conducted (norms) and how they believed research *is* conducted (practice) using an online survey. 
## RESULTS: We found that XXX. . .
## CONCLUSION:

Keywords: open science, psychology, teaching, reproducibility, replication
wordcount: X

bibliography: ['r-references.bib','Undergrads & Open Science (public).bib']
floatsintext: yes
figurelist: no
tablelist: no
footnotelist: no
linenumbers: yes
mask: yes
draft: no
documentclass: apa6
classoption: man
affiliation:
- id: '1'
  institution: Swinburne University of Technology
- id: '2'
  institution: Massey University
---
<!-- I've only partially entered authorship deets for the moment and set it to mask authorship info when knitting
It's set to default to knit to .docx, but can also knit to pdf (if you have a tex distro installed)
The pdf looks nicer and might be good for a preprint but .docx probably easiest to use for journal submissions.
To knit to RMarkdown you will probably need the papaja package installed, and to knit to .pdf you will need a tex distro (e.g., TinyTex).
However, it is possible to run all the R code (without knitting to .docx or .pdf) by clicking Run > Run All Chunks Below.
This could be useful in future for readers interested in reproducing results but who don't have or wish to install 
papaja and its many dependencies.
-->

@@

# # import the metadata [check if I need it for these analyses?]
# metadata <- here::here("survey", "data", "os_metadata_raw_data.csv") %>% 
#   read_csv(col_names = TRUE, skip_empty_rows = TRUE) %>% 
#   filter(!is.na(OldVariable))
```

@@

The most comprehensive set of principles for how science *ought* to be practiced are Merton's norms of science [@mertonNoteScienceDemocracy1942]. Scientists [@andersonExtendingMertonianNorms2010] and graduate students [@andersonGraduateStudentExperience1994] alike have historically endorsed the normative value of Merton's principles. Furthermore, many of the recent practices designed to make science more transparent and open reflect Mertonian norms [see @vazireWeWantBe; vazireWhereAreSelfcorrecting2020]. For example, the practice of sharing open source software corresponds to the Mertonian norm of *communism*: Scientists should have common ownership of scientific goods. Similarly, the practices of sharing of preprints for open peer review and open data for checking of reproducibility corresponds to the norm of communality, and also to that of *organised skepticism*: Scientific claims should be subjected to critical scrutiny. Preregistration can be connected to the norm of *disinterestedness*: By making (and preregistering) decisions about how to analyse data before results are produced, a researcher can limit the degree to which the substantive results produced by different analytic strategies affect their decisions regarding which analyses to report. In this sense, the ongoing reform in psychological research can partly be understood as simultaneously a set of new practices and a re-affirmation of established norms.

@@

@@

@@

@@

Of the remaining `r n` participants, most reported being
18-24 years old (*n* = `r age[1,2]`), `r age [2,2]` 
reported that they were 25-34 years old, `r age [3,2]` were 35-44 years old,
`r age [4,2]` were 45-54 years old, and `r age [5,2]` was 55-64 years old.

The majority of participants (*n* = `r gender[1,2]`) reported that they were female, 
`r gender[2,2]` reported that they were male, `r gender[3,2]` participants reported 
their gender identity as "queer man", and `r gender[3,2]` participants reported 
non-binary gender.^[While the response "queer man" could potentially be coded as
"male", we are aware that some individuals who report gender in this way would
not feel that such reclassification was appropriate. We have retained the original
response in order to provide a faithful representation of the participant's 
self-reported gender.]

@@

```{r qual responses}

# [breadcrumbs] 
 # once qual responses are coded, I will need to return here to 
 # include details about which univrsity the participant is enrolled in
 # name of qualification
 # major [how many are majoring in psyc; NAs; will decide later?]

@@

Our approach to measuring norms and counternorms focussed on participants' evaluation of ten specific open science practices that reflected diverse open science norms rather than trying to measure endorsement of the more abstract Mertonian norms (cf. Anderson et al., 2007). <!-- Mention here our discussions workshopping of common open science norms at SIPs? ! -->
The practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficient information of replicability, preprints, open materials, open data, and open access publishing. Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." Although we acknowledge the existence of important debate about the merits of some of these practices [e.g., @TQMP16-4-376, @rubinWhenDoesHARKing2017, @szollosiPreregistrationWorthwhile2020], we selected the items to be emblematic of common concerns in the open science movement.

@@

<!-- Add Table X of norms and counternorms statements that map to each practice -->

@@

knitr::kable(norm_items,
             caption = "Norm and counternorm items",
             align = c('lll'))
```

@@

## Data analysis

@@

@@

```{r correlation_matrix}
#pairs.panel etc. won't really work because there are too many variables
#And we only need corrs between matched pairs
#So doing this a bit more manually
layout(matrix(1:8, ncol = 4))

plot(df$critical_norm ~ jitter(df$critical_cnorm), xlab = "critical counternorm", ylab = "critical norm")
abline(lm(df$critical_norm ~ df$critical_cnorm), col = "blue")
legend(x='bottomright', legend=paste('Cor =', round(cor(df$critical_norm, df$critical_cnorm),2)))

plot(df$prereg_norm ~ jitter(df$prereg_cnorm), ylab = "Prereg norm", xlab = "Prereg counternorm")
abline(lm(df$prereg_norm ~ df$prereg_cnorm), col = "blue")
legend(x='bottomright', legend=paste('Cor =', round(cor(df$prereg_norm, df$prereg_cnorm),2)))

plot(df$reg_report_norm ~ jitter(df$reg_report_cnorm), ylab = "Reg Reports norm", xlab = "Reg Reports counternorm")
abline(lm(df$reg_report_norm ~ df$reg_report_cnorm), col = "blue")
legend(x='bottomleft', legend=paste('Cor =', round(cor(df$reg_report_norm, df$reg_report_cnorm),2)))

plot(df$phack_norm ~ jitter(df$phack_cnorm), ylab = "p-hacking rnorm", xlab = "p-hacking counternorm")
#potential confusion here about direction of phrasing (pro p-hacking = counternorm?)
abline(lm(df$phack_norm ~ df$phack_cnorm), col = "blue")
legend(x='bottomleft', legend=paste('Cor =', round(cor(df$phack_cnorm, df$phack_norm),2)))

plot(df$hark_norm ~ jitter(df$hark_cnorm), ylab = "HARKing norm", xlab = "HARKing counternorm")
abline(lm(df$hark_norm ~ df$hark_cnorm), col = "blue")
legend(x='bottomright', legend=paste('Cor =', round(cor(df$hark_cnorm, df$hark_norm),2)))

plot(df$info_for_rep_norm ~ jitter(df$info_for_rep_cnorm), ylab = "Replicability norm", xlab = "Replicability counternorm")
abline(lm(df$info_for_rep_norm ~ df$info_for_rep_cnorm), col = "blue")
legend(x='right', legend=paste('Cor =', round(cor(df$info_for_rep_norm, df$info_for_rep_cnorm),2)))

plot(df$preprint_norm ~ jitter(df$preprint_cnorm), ylab = "Preprints norm", xlab = "Preprints counternorm")
abline(lm(df$preprint_norm ~ df$preprint_cnorm), col = "blue")
legend(x='bottomleft', legend=paste('Cor =', round(cor(df$preprint_norm, df$preprint_cnorm,
                                                       use = "pairwise.complete.obs"),2)))

plot(df$open_materials_norm ~ jitter(df$open_materials_cnorm), ylab = "Open materials norm", xlab = "Open materials counternorm")
abline(lm(df$open_materials_norm ~ df$open_materials_cnorm), col = "blue")
legend(x='bottomleft', legend=paste('Cor =', round(cor(df$open_materials_norm, df$open_materials_cnorm, use = "pairwise.complete.obs"),2)))

plot(df$open_data_norm ~ jitter(df$open_data_cnorm), ylab = "Open data norm", xlab = "Open data counternorm")
abline(lm(df$open_data_norm ~ df$open_data_cnorm), col = "blue")
legend(x='bottomleft', legend=paste('Cor =', round(cor(df$open_data_norm, df$open_data_cnorm),2)))

plot(df$open_access_norm ~ jitter(df$open_access_cnorm), ylab = "Open access norm", xlab = "Open access counternorm")
abline(lm(df$open_access_norm ~ df$open_access_cnorm), col = "blue")
legend(x='bottomright', legend=paste('Cor =', round(cor(df$open_access_norm, df$open_access_cnorm),2)))

@@

<!-- Add another paragraph here to elaborate on the shape of these distributions to help interpret the above point of discussion.-->

@@

## The replication crisis
Interestingly, the vast majority of participants had not heard of "the replication crisis" <!-- add numeric estimate-->.

<!-- For people who answered "yes" (they had heard the term) there were a couple of open-ended follow-up items: What do you think the replication is? Which scientific disciplines do you think are most affected by the replication crisis? We could analyse these and try to give some indication of whether the students who *had* heard of it actually knew what the term refers to. -->

Participants' estimates of the replicability of psychological studies was near the midpoint of the possible range <!-- about 56% - need to code this in--> .

<!--Point for discussion: Interestingly, this estimate is fairly consistent (albeit perhaps slightly more optimistic) than empirical estimates from large-scale studies. However, it could plausibly simply reflect a great deal of uncertainty on the part of participants.
-->

<!-- ☐ On the above point, Comment here on the shape of the distribution for this question. -->

@@

Despite efforts to popularize the replicability of research the past decade, and despite popular media attention, most incoming psychology students in our sample were unaware of the replication crisis. Encouragingly, on the other hand, most tended to endorse open science norms more-so than counternorms, although this wasn't the case for all open science practices (namely sharing of pre-prints and avoiding HARKing). IIt may be interesting to consider whether student norms regarding the sharing of pre-prints would be expected to have shifted since this data was collected given the rapid increase in the dissemination of pre-prints related to COVID-19.

@@

@@

## Limitations, strengths, and future directions

Despite a relatively large sample size, our results provide an imperfect picture of new psychology students’ methodological understandings. Our use of convenience samples coupled with the imprecision of polling students’ impressions at one point in time suggest that we can make only very tentative generalisations to a wider population of incoming psychology students. However, collectively these results demonstrate some clear topics that might be targeted in our teaching: for example, emphasising the value of pre-prints and open-data to research practice.

Our questions focused primarily on attitudes and beliefs so that we could better document the implicit understanding that guided students’ thoughts about the research process. However, we did not probe students' factual knowledge of methodological findings or concepts. It’s quite possible that reform in secondary school instruction has improved students’ understandings of more fundamental statistical (e.g., confidence interval estimation) and design (e.g., direct replications) open science considerations without necessarily impacting their attitudes and beliefs. Yet, research at the tertiary level casts doubt that the disciplinary reform from the past 2 decades has had much impact on the content of our teaching (Friedrich et al., 2018).

<!--
More to say here.
-->

@@

@@

>>>>

---
title: What do incoming university students believe about open science practices in
  psychology?
author:
- name: Jennifer L. Beaudry
  affiliation: '1'
  corresponding: yes
  address: Postal address
  email: jbeaudry@swin.edu.au
  role: null
- name: Michael C. Philipp
  affiliation: '2'
  role: null
- name: Matt N. Williams
  affiliation: '2'
  role: null
- name: Emily Kothe
  affiliation: '3'
  role: null
shorttitle: Psychology students' beliefs about open science
output:
  papaja::apa6_word: default
  papaja::apa6_pdf: default
authornote: |
  1 Flinders University, Australia
  2 Massey University, New Zealand
  3 Deakin University, Australia
abstract: |
## BACKGROUND: Rapid changes to methodological best practices present significant challenges for educating students new to the field of psychology. Some students may have existing knowledge about recent methodological reforms (e.g., preregistration, replication). Yet, where knowledge is lacking, overemphasizing the problems that precipitate these reforms (e.g., p-hacking, HARKing) may lead students to de-value scientific methods as a credible means for generating knowledge. 
## OBJECTIVE: Understanding students’ naive conceptions about how science works and the norms that guide scientific best practice is important so that teachers can adapt their teaching to the students’ existing understandings. 
## METHOD: This study examined ### incoming undergraduate psychology students’ understandings of how research *should* be conducted (norms) and how they believed research *is* conducted (practice) using an online survey. 
## RESULTS: We found that XXX. . .
## CONCLUSION:

keywords: open science, psychology, teaching, reproducibility, replication
wordcount: X
bibliography: ['r-references.bib','Undergrads & Open Science (public).bib']
floatsintext: yes
figurelist: no
tablelist: no
footnotelist: no
linenumbers: yes
mask: yes
draft: no
documentclass: apa6
classoption: man
affiliation:
- id: '1'
  institution: Swinburne University of Technology
- id: '2'
  institution: Massey University
editor_options: 
  chunk_output_type: console
---

<!--
Teaching in Psychology ask for structured abstracts - 'For these types of article submissions, please include (in this order) a section on the background, objective(s), method, results, conclusion, and teaching implications.' 200 word limit
The abstract also doesn't currently knit into the final document for some reason?

<!-- I've only partially entered authorship deets for the moment and set it to mask authorship info when knitting
It's set to default to knit to .docx, but can also knit to pdf (if you have a tex distro installed)
The pdf looks nicer and might be good for a preprint but .docx probably easiest to use for journal submissions.
To knit to RMarkdown you will probably need the papaja package installed, and to knit to .pdf you will need a tex distro (e.g., TinyTex).
However, it is possible to run all the R code (without knitting to .docx or .pdf) by clicking Run > Run All Chunks Below.
This could be useful in future for readers interested in reproducing results but who don't have or wish to install 
papaja and its many dependencies.
-->

@@

# import the metadata 
#metadata <- here::here("survey", "data", "students_metadata.csv") %>% 
 #read_csv(col_names = TRUE, skip_empty_rows = TRUE) %>% 
 #filter(!is.na(old_variable)) %>% 
 #dplyr::select (-c("...10", "note:"))

#MW: I have commented this chunk out out temporarily because it might need tweaking - it assumes a subfolder in "survey" called "data"
#and the last select line doesn't seem to run (no column with that name recognised)
```

@@

The most comprehensive set of principles for how science *ought* to be practiced are Merton's norms of science [@mertonNoteScienceDemocracy1942]. Scientists [@andersonExtendingMertonianNorms2010] and graduate students [@andersonGraduateStudentExperience1994] alike have historically endorsed the normative value of Merton's principles. Furthermore, many of the recent practices designed to make science more transparent and open reflect Mertonian norms [see @vazireWeWantBe2019; @vazireWhereAreSelfcorrecting2020]. For example, the practice of sharing open source software corresponds to the Mertonian norm of *communism*: Scientists should have common ownership of scientific goods. Similarly, the practices of sharing of preprints for open peer review and open data for checking of reproducibility corresponds to the norm of communality, and also to that of *organised skepticism*: Scientific claims should be subjected to critical scrutiny. Preregistration can be connected to the norm of *disinterestedness*: By making (and preregistering) decisions about how to analyse data before results are produced, a researcher can limit the degree to which the substantive results produced by different analytic strategies affect their decisions regarding which analyses to report. In this sense, the ongoing reform in psychological research can partly be understood as simultaneously a set of new practices and a re-affirmation of established norms.

@@

<!--I feel like citing tweets is going to cause arguments with a reviewer, but not sure what else to do here.-->

@@

<!-- I wonder about saying something somewhere about how the items we developed (and openly shared) in this study could be useful for teachers who might wish to assess their own students' beliefs about open science practices in psychology?
Also, if anyone else has any good citations on the value of exploratory research, can you let me know?
-->

@@

<!-- It's common to put participants first, but might the description flow more smoothly if we put that short Procedure subsection first? That way they know how we recruited people before we get to thinks like exclusions and screening -->

@@

Most participants reported that they were
18-24 years old (*n* = `r age[1,2]`), `r age [2,2]` 
reported that they were 25-34 years old, `r age [3,2]` were 35-44 years old,
`r age [4,2]` were 45-54 years old, and `r age [5,2]` was 55-64 years old. The majority of participants (*n* = `r gender[1,2]`) reported that they were female, 
`r gender[2,2]` reported that they were male, `r gender[3,2]` participant reported 
their gender identity as "queer man", and `r gender[3,2]` participant reported 
non-binary gender.

<!--We had a footnote here (below) but given the word limit it might be safely left out unless a reviewer queries it...

^[While the response "queer man" could potentially be coded as
"male", we are aware that some individuals who report gender in this way would
not feel that such reclassification was appropriate. We have retained the original
response in order to provide a faithful representation of the participant's 
self-reported gender.] -->

@@

<!--
MP: Seems like we are missing some nationalities here – US nationalities? NZ? Or is this just the top 3?
-->

@@

Our approach to measuring norms and counternorms focussed on participants' evaluation of ten specific open science practices that reflected diverse open science norms rather than trying to measure endorsement of the more abstract Mertonian norms (cf. Anderson et al., 2007). <!-- Mention here our discussions workshopping of common open science norms at SIPs? ! -->
The open science practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficent information of replicability, preprints, open materials, open data, and open access publishing. Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." Although we acknowledge the existence of important debate about the merits of some of these practices [@TQMP16-4-376; @rubinWhenDoesHARKing2017; @szollosiPreregistrationWorthwhile2020], we selected the items to be emblematic of common concerns in the open science movement.

@@

<!-- Add Table X of norms and counternorms statements that map to each practice 
MW: The table captions/crossreferences may not be working - see the compiled document.
-->

@@

# [breadcrumb Sept 10: pull in this info from the meta data]

# recode the data so the response options have proper labels

# c <- metadata %>% 
#     filter(Scale == "OSmost") %>% 
#     filter(NewVariable != "OSmost_text") #remove this value from metadata
# 
# d <- full_join(OSmost_long, c, by = c("OSmost" = "NewVariable")) %>% 
#   rename ("OSmost_label" = "ItemText")

norm_items_wide <- pivot_wider(
  norm_items,
  names_from = Category,
  values_from = Item)

knitr::kable(norm_items_wide,
             caption = "Norm and counternorm items",
             align = c('lll'))
```

@@

<!--MW: We need to add in the actual numbers of collaborators/institutions above - we should have a record somewhere in our Google Drive-->

## Data analysis
<!--MW: We had this subheading in here but might not need it? The analysis is pretty clear from the descripion below-->

@@

<!--MW: The paragraphs above contain some numeric info that's written in manually rather than being R outputs (e.g., "three", "seven") 
Not sure if that's a worry.
-->

@@

```{r norms in practice}

# select columns that relate to norms in practice & pivot it long & drop the na values
in_prac_long <- df %>% 
  dplyr::select(c(id,preregistration:open_access)) %>% 
      pivot_longer (cols = -id,
                names_to = "practice",
                values_to = "prevalence rating") %>% 
  drop_na()

# get the n values for each of the practices
in_prac_counts <- in_prac_long %>% 
  dplyr::group_by(practice) %>% 
  count() %>% 
  ungroup()

# calculate means
in_prac_ms_sds <- in_prac_long %>%
  dplyr::group_by(practice) %>%
  summarise(mean = mean(`prevalence rating`),
            sd = sd(`prevalence rating`)) %>%
  ungroup()

# join the n values with the means
in_prac_means <- in_prac_counts %>% inner_join(in_prac_ms_sds)

# calculate 95% CIs
error <- qnorm(0.975) * in_prac_means$sd/sqrt(in_prac_means$n)
in_prac_means$lower <- in_prac_means$mean - error
in_prac_means$upper <- in_prac_means$mean + error

# combine means & SDs
in_prac_means$`Prevalence Ratings` <- paste0(round_tidy(in_prac_means$mean,2),
                          " (", 
                          round_tidy(in_prac_means$sd,2),
                            ")", 
                            " [",
                            round_tidy(in_prac_means$lower,2),
                            ", ", 
                            round_tidy(in_prac_means$upper,2),
                            "]")

# clean it up into a new dataframe with only the columns we need
in_practice_means <- in_prac_means %>% 
  dplyr::select(practice, `Prevalence Ratings`) %>% 
  rename(Practice = practice)

# breadcrumbs:
# I need to use apa_tables.... (in line with papaja)
# update practice descriptions so they make sense to readers

knitr::kable(in_practice_means,
             caption = "Means, standard deviations, and 95% confidence intervals for the prevalence ratings for each research practice",
             digits = 2,
             align = c('lc'))

@@

We can add a table here with descriptive statistics (means? more?) for the norms in practice items.

@@

## The replication crisis
Interestingly, only `r round(sum(df$crisis==1, na.rm = TRUE)/length(df$crisis)*100, 0)`% of participants indicated they had heard of "the replication crisis", with `r round(sum(df$crisis==2, na.rm = TRUE)/length(df$crisis)*100, 0)`% indicating that they had not heard of the crisis and `r round(sum(is.na(df$crisis))/length(df$crisis)*100, 0)`% missing.

Participants who indicated they had heard of the replication crisis were asked what "What do you think 'the replication crisis' is"? Of the `r length(df$crisis_text[is.na(df$crisis_text)==FALSE])` participants who answered this question, most provided responses roughly consistent with the conventional interpretation of the term. Example responses included "The crisis where most studies were unable to be replicated when researchers decided to replicate previously done studies" and "Where previously trusted studies have been replicated the results were not able to be replicated". Only `r sum(crisis_descriptions$Accurate == "n")` responses were suggestive of a misunderstanding of the term (e.g., "Plagiaris[m]", "only same results being published").

Participants' estimates of the replicability of psychological studies were variable. The mean, _M_ =`r mean(df$rep_perc, na.rm = TRUE)` was near the midpoint of 50%, but with substantial variability around this estimate, _SD_ = `r sd(df$rep_perc, na.rm = TRUE)`, minimum = `r min(df$rep_perc, na.rm = TRUE)`,  maximum = `r max(df$rep_perc, na.rm = TRUE)`. A histogram of participants' responses is provided in Figure X.

```{r rep_perc_histogram}
hist(df$rep_perc, main = NULL, xlab = "Percentage")
```
_Figure X_. Histogram of participants' responses to the question: "Imagine that a set of researchers select 100 published studies about psychology, and repeat each study again, exactly how it was described in the original report but with a new set of participants. We call repeating a study like this a “replication study”. At a guess, how many of these replication studies do you think would produce the same conclusions as the original studies?" Responses provided on a visual slider.

<!-- Participants were also asked "Which scientific disciplines do you think are most affected by the replication crisis?" As we discussed, I'm not sure this response will really be useful to look at given that we have "primed" them to think of psychology as being most affected (and indeed that's what the responses largely indicate).-->

@@

Despite efforts to popularize the replicability of research the past decade, and despite popular media attention, most incoming psychology students in our sample were unaware of the replication crisis. Encouragingly, on the other hand, most tended to endorse open science norms more-so than counternorms. Notably this wasn't the case for all open science practices (namely sharing of pre-prints and avoiding HARKing). It may be interesting to consider whether student norms regarding the sharing of pre-prints would be expected to have shifted since this data was collected given the rapid increase in the dissemination of pre-prints related to COVID-19. On the other hand, it may well be that scientific training has enshrined the practices of peer review and generating hypotheses after analyses (e.g., Bem, 2004) as essential scientific practices that are robust to change.

<!--Bem begins his guide for writing articles as, “There are two possible articles you can write: (a) the article you planned to write when you designed your study or (b) the article that makes the most sense now that you have seen the results. They are rarely the same, and the correct answer is (b).”-->

@@

<!-- MW: Should that last bit say registered reports?
There's also quite a bit of manually written numeric info here - we should probably convert that to R code?
-->

@@

<!-- Since the journal asks for a Teaching Implications subsection in the structured abstract, I'm thinking it'd make sense to have a Teaching Implications subsection in the discussion, about here? -->

## Strengths and limitations
Despite a relatively large sample size, our results provide an imperfect picture of new psychology students’ methodological understandings. Our use of convenience samples coupled with the imprecision of polling students’ impressions at one point in time suggest that we can make only very tentative generalisations to a wider population of incoming psychology students. However, collectively these results demonstrate some clear topics that might be targeted in our teaching: for example, emphasising the value of pre-prints and open-data to research practice.

Our questions focused primarily on attitudes and beliefs so that we could better document the implicit understanding that guided students’ thoughts about the research process. However, we did not probe students' factual knowledge of methodological findings or concepts. It’s quite possible that reform in secondary school instruction has improved students’ understandings of more fundamental statistical (e.g., confidence interval estimation) and design (e.g., direct replications) open science considerations without necessarily impacting their attitudes and beliefs. Yet, research at the tertiary level casts doubt that the disciplinary reform from the past 2 decades has had much impact on the content of our teaching [@friedrichReplicatingNationalSurvey2018].

<!--
MW: The bit from "It's quite possible..." is sensible, but if needed could possibly shave some words off by excluding? 
See how we go when we check full word count
-->

@@

# Supplemental Materials

Figure XX displays the histograms for each of the norms in practice items.

```{r norms in practice histogram}

p <- in_prac_long %>%
  ggplot(aes(x = `prevalence rating`)) +
  geom_histogram(aes(y=stat(count)), binwidth = 10) +
    xlab("Prevalence Ratings (%)") +
    ylab("Frequency") +
    theme_classic () +
    theme(axis.text = element_text(size = 9), axis.title = element_text(size = 9)) +
    facet_wrap(~practice, nrow = 2)
p

#[breadcrumb: need to update the theme & the practice names]

@@

<!-- This is nice to do, but it generate a 150+ word paragraph of citations to packages, including citations to packages our code doesn't directly use (e.g. nlme, multilevel, etc.). We might need to cut it down manually to a more concise list?
-->
